Music Perception 2: Questionnaire

### 2021-05-10 analysis/questionnaire.Rmd
upload questionnaire summary (up to 14)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Music Perception: Questionnaire"
output: html_notebook
---

@@

# extract the total number of years of training for the longest instrument (input manually based on the original csv file)
dt$Training <- c(7, 7, 10, 6, 7, 6, 6, 20, 12, 7, 7, 11, 9, 16, 20, 15, 19, 14, 24, 12, 14)

# exclude participants
dt_included <- dt[SubNr != 9]

>>>>

---
title: "Music Perception 2: Questionnaire"
output: html_notebook
---

@@

# extract the total number of years of training for the longest instrument (input manually based on the original csv file)
dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20)

# exclude participants
dt_included <- dt[SubNr != 4]
